A 38 Million Year Old Mini-Neptune in the Kepler Field

### 2021-09-29 paper/ms.tex
update ms
Moved appendix material around, per LAH suggestion.

Co-authored-by: Lynne Hillenbrand <lah@astro.caltech.edu>

\title{
  %Kepler 1627Ab: A 38 Million Year Old
  %Kepler 1627 Ab:
  A 38 Million Year Old Mini-Neptune in the Kepler Field
}

@@

% 208 words (250 max)
\begin{abstract}
  Kepler\,1627A is a G8V star previously known to host a
  $3.4\,R_\oplus$ mini-Neptune on a 7.2\,day orbit.  The star was
  observed by the Kepler space telescope because it is nearby
  ($d=329\,{\rm pc}$) and it resembles the Sun.  Here we show
  using Gaia kinematics, TESS stellar rotation periods, and
  spectroscopic lithium abundances that Kepler\,1627 is a member of
  the \clusterage\ old $\delta$~Lyr cluster.  To our knowledge, this makes
  Kepler\,1627Ab the youngest planet with a precise age yet found
  by the main Kepler mission.
  The Kepler photometry shows two 
  peculiarities: the average transit profile appears to be
  asymmetric, and the individual transit times are correlated with the local light curve slope.
  % The former could be explained by a dusty atmospheric outflow; the
  % latter could be explained by unresolved starspot crossings of a
  % planet on a prograde orbit.  
  We discuss possible explanations for these anomalies, and
  highlight broader implications for our ability to expand the census
  of age-dated planets.
\end{abstract}

@@

\begin{figure}[t]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.49\textwidth]{f1.pdf}
	\end{center}
	\vspace{-0.7cm}
	\caption{
    {\bf Kepler's view of the $\delta$~Lyr cluster.} Each black circle is a
    candidate cluster member, selected from the catalog of \citet{KounkelCovey2019} based on its
    position and kinematics.
    Of the \nkinematic\ candidate cluster members, 58 have at least one
    quarter of Kepler data.  TESS has also observed most of the
    cluster, for one to two lunar months to date.
		\label{fig:skychart}
	}
\end{figure}

Matching our young star list against stars observed by Kepler yielded
%two discoveries.  The first, to be discussed in an upcoming analysis
%by J.~Curtis et al{.}, is that Kepler observed the $\approx$350\,Myr
%open cluster Theia~520 (UBC~1).  At least six Kepler planets are known
%in the cluster from the Kepler-52 and Kepler-968 systems
%\citep{rowe_validation_2014,jontof-hutter_following_2021}.  The second
%discovery, and the focus of this work, is
the discovery that Kepler observed a portion of the \cn\ (Stephenson-1; Theia~73; \citealt{stephenson_possible_1959}).
Figure~\ref{fig:skychart} shows the overlap between the Kepler field
and the cluster.  A previous clustering analysis of the Gaia
data by \citet{kounkel_untangling_2019}
reported that Kepler\,1627 (KIC 6184894; KOI 5245; TIC 120105470) is a
member of the \cn.  Given the
previous statistical validation of the close-in mini-Neptune Kepler
1627b
\citep{2012ApJS..199...24T,morton_false_2016,thompson_planetary_2018},
we examined the age of the star and its putative host cluster more
closely (Section~\ref{sec:cluster}).  We find that the $\delta$ Lyr
cluster is \clusterage\ old, and that \sn\ is indeed a member of the
cluster.  Focusing on the planet itself, we confirm that despite the
presence of a previously unreported binary companion, hereafter
Kepler\,1627B, the planet orbits the G-dwarf primary, Kepler\,1627A
(Section~\ref{sec:planet}).  Based on a correlation between the
planetary transit times and the local light curve slope, the orbit
also seems to be prograde.  We conclude by highlighting broader
implications for our ability to age-date a larger sample of planets
(Section~\ref{sec:conc}).

@@

@@

To assess the age of the cluster and our star of interest, we used a
combination of isochronal, gyrochronal, and lithium-based
age-dating.

\subsection{Color-Absolute Magnitude Diagram}
\label{sec:camd}

We measured the isochrone age through an empirical approach.  The left
panel of Figure~\ref{fig:age} shows the color-absolute magnitude
diagram (CAMD) of stars in the \cn, IC\,2602, the Pleiades, and the
field.  The candidate \cn\ members shown are selected based on their
positions and kinematics (see Appendix~\ref{app:kinematicselection}).
Those from the Pleiades and IC\,2602 are adopted from
\citet{cantatgaudin_gaia_2018}, and the field stars are from the Gaia
EDR3 Catalog of Nearby Stars \citep{gaia_gcns_2021}.  We cleaned these
following the data filtering criteria discussed in Appendix~B of
\citet{GaiaCollaboration2018}, except that we weakened the parallax
precision requirement to $\varpi/\sigma_\varpi>5$.  These filters were
designed to include genuine binaries while omitting instrumental
artifacts.  We then corrected for extinction by querying the
3-dimensional maps of \citet{capitanio_threedimensional_2017} and
\citet{lallement_threedimensional_2018}\footnote{\url{https://stilism.obspm.fr/}, 2021/09/25},
and then applied the extinction coefficients $k_X\equiv A_X/A_0$
computed by \citet{GaiaCollaboration2018} and assumed that $A_0 = 3.1
E(B-V)$.  For IC\,2602, the Pleiades, and the \cn, this procedure
yielded a respective mean and standard deviation for the reddening of
$E(B-V)=\{0.020\pm0.003, 0.045\pm0.008, 0.032\pm0.006\}$.  These
values agree reasonably well with previously reported values from the
literature \citep[{\it
e.g.},][]{GaiaCollaboration2018,kounkel_untangling_2019,bossini_age_2019}.

@@

The ages returned by this procedure depend on the ages assumed for
each reference cluster.  We adopted a 115\,Myr age for the Pleiades \citep{dahm_2015},
and a 16\,Myr age for UCL \citep{pecaut_star_2016}.  The age
of IC\,2602 however is the most important ingredient, since it
receives the most weight in the interpolation.  Plausible ages for
IC\,2602 span 30\,Myr to 46\,Myr, with slightly older ages being
preferred by the lithium-depletion-boundary (LDB) measurements 
\citep{dobbie_ic_2010,randich_gaiaeso_2018}
and
younger ages by the main-sequence turn-off
\citep{stauffer_rotational_1997,david_ages_2015,bossini_age_2019}.
If we were to adopt the 30\,Myr age for IC\,2602, then the \cn\ would
be $31^{+5}_{-4}$\,Myr old.  For the converse extreme of 46\,Myr, the
\cn\ would be $44^{+8}_{-7}$\,Myr old.  We adopt an intermediate
38\,Myr age for IC\,2602, which yields an age for the \cn\ of
\clusterage.\footnote{Our exploration of the PARSEC and MIST isochrone
models over a grid of ages, metallicities, and reddenings, yielded the
best agreement for this $\approx 38\,$Myr age as well, given ${\rm
[Fe/H] = +0.1}$ and $A_V=0.2$
\citep{bressan_parsec_2012,choi_mesa_2016};  this preferred CAMD
reddening is higher than the \citet{lallement_threedimensional_2018}
value by a factor of two.  } Follow-up studies of the LDB or
main-sequence turn-off in the \cn\ could help determine a more precise
and accurate age for the cluster, however these are beyond our scope.

\subsection{Stellar Rotation Periods}

@@

We then cleaned the candidate TESS rotation period measurements
through a combination of automated and manual steps.  As a matter of
scope, we restricted our attention to the \nkinwithtess\ stars
discussed in Appendix~\ref{app:kinematicselection} in the spatial and
kinematic proximity of Kepler\,1627.  To avoid blending, we also only
focused on stars for which no companions were known with a brightness
exceeding one-tenth of the target star in a $21\farcs0$ radius.  There
were \nkinwithtessandcrowding\ stars that met these requirements, and
that had TESS data available.  For plotting purposes we then imposed a
selection based on the strength of the signal itself: we required the
Lomb Scargle power to exceed 0.2, and the period to be below 15\,days.

The lower panel of Figure~\ref{fig:age} shows the resulting
\nkindefaultcleaning\ stars.  The majority of these stars fall below
the ``slow sequence'' of the Pleiades, consistent with a
gyrochronological age for the \cn\ below 100\,Myr.  Approximately 10
stars appear as outliers above the ``slow sequence''.  Assuming that
they are all false positives ({\it i.e.}, field interlopers), the
rotation period detection fraction would be
$\nrotgood/\nkinwithtessandcrowding \approx \nfracprot\%$.  The
rotation period distributions of other 30\,Myr to 50\,Myr clusters
({\it e.g.}, IC\,2602 and IC\,2391) are indistinguishable
\citep{douglas_stephanie_t_2021_5131306}.  While binarity is known to
affect the density of stars that fall beneath the slow sequence
\citep{meibom_effect_2007,gillen_ngts_2020,bouma_2021_ngc2516}, it is
not expected to change the central conclusion regarding the cluster's
age.
%%VERSION1
%Based on an analysis of photometric binaries and stars with high RUWE,
%we found evidence for similar effects to those previously noted in the
%literature.  However, since the purpose of our rotation period
%analysis is to determine the age of the \cn, we do not dwell on this
%topic.
% %VERSION0
% Appendix~\ref{app:rotationbinarity} discusses this topic, and finds
% evidence for similar effects to those previously noted in the
% literature.

\subsection{Age of Kepler\,1627}

To summarize, the age of the \cn\ based on the empirical
pre-main-sequence interpolation method is \clusterage.  This method
hinges on the age adopted for IC\,2602, since it is the closest
reference cluster in the color-absolute magnitude diagram.
Gyrochronologically, while most of the FGK dwarfs in the \cn\ have not
yet converged to a slow sequence, their rotation periods are generally
consistent with a $\approx40$\,Myr age. The most precise age for \sn\ and its
planet are therefore identical to the cluster, based on the star's
spatial and kinematic association with the cluster, and the assumption
that the planet formed shortly after the star.

Beyond the kinematic and rotational lines of evidence for the youth of
\sn, there is a final consistency check: the abundance of
Li\,\textsc{I} as inferred from the 6708\,\AA\ doublet \citep[{\it
e.g.},][]{soderblom_ages_2014}.  We acquired an iodine-free spectrum
from Keck/HIRES on the night of 2021 March 26 using the standard setup
and reduction techniques of the California Planet Survey
\citep{howard_cps_2010}.  Following the equivalent width measurement
procedure described by \citet{bouma_2021_ngc2516}, we find ${\rm
EW}_{\rm Li} = 233^{+5}_{-7}$\,m\AA.   %Note that this value does not
%correct for the Fe\,\textsc{I} blend at 6707.44\AA. 
Given the effective temperature of \sn\ (Table~\ref{tab:starparams}),
this measurement is in agreement with expectations for a $\approx40$\,Myr star
({\it e.g.}, as measured in IC~2602 by
\citealt{randich_gaiaeso_2018}).  It is also larger than any
lithium equivalent widths measured by \citet{berger_identifying_2018}
in their analysis of 1{,}301 Kepler-star spectra.

@@

		\vspace{-0.2cm}	
		\subfloat{
			\includegraphics[width=0.5\textwidth]{f3b.pdf}
			\includegraphics[width=0.5\textwidth]{f3c.pdf}
		}
	\end{center}
	\vspace{-0.7cm}
  \caption{ {\bf The light curve of Kepler\,1627.}
    {\it Top}: 
    The Kepler data span 1{,}437 days (3.9 years), sampled at
    30 minute cadence;  a 100 day segment is shown.  The
    top panel shows the \texttt{PDCSAP} median-subtracted flux in
    units of parts-per-thousand ($\times 10^{-3}$).  The dominant
    signal is induced by starspots.  The stellar
    variability model (orange line) is subtracted below, revealing the
    transits of \pn.  The
    online Figure Set spans the entire 3.9 years of observations.
    {\it Bottom}:
    Phase-folded transit of Kepler 1627Ab with stellar variability
    removed.  Windows over 20 hours ({\it left}) and the entire orbit
    ({\it right}) are shown, and the residual after subtracting the
    transit is in the bottom-most row.  The 2-$\sigma$ model uncertainties
    and the best-fit model are the light purple band and the dark
    purple line.  Gray points are individual flux measurements; black
    points bin these to 20 minute intervals, and have a representative
    1-$\sigma$ error bar in the lower right of each panel.  The
    asymmetric residual during transit appears to be robust to
    different detrending methods.
    \label{fig:lc}
  }
\end{figure*}

\begin{figure}[tp]
	\begin{center}
		\leavevmode
		\subfloat{
			\includegraphics[width=0.49\textwidth]{f4a.pdf}
		}

>>>>

\title{
  %Kepler 1627Ab: A 38 Million Year Old
  %Kepler 1627 Ab:
  %A Mini-Neptune in the Kepler Field Only 38 Million Years Old
  A 38 Million Year Old Mini-Neptune in the Kepler Field
}

@@

% 208 words (250 max)
\begin{abstract}
  Kepler\,1627A is a G8V star previously known to host a
  $3.4\,R_\oplus$ mini-Neptune on a 7.2\,day orbit.  The star was
  observed by the Kepler space telescope because it is nearby
  ($d=329\,{\rm pc}$) and it resembles the Sun.  Here we show
  using Gaia kinematics, TESS stellar rotation periods, and
  spectroscopic lithium abundances that Kepler\,1627 is a member of
  the \clusterage\ old $\delta$~Lyr cluster.  To our knowledge, this makes
  Kepler\,1627Ab the youngest planet with a precise age yet found
  by the main Kepler mission.
  The Kepler photometry shows two 
  peculiarities: the average transit profile appears to be
  asymmetric, and the individual transit times are correlated with the
  local light curve slope.
  We discuss possible explanations for each anomaly.
  More widely applicable though is the fact that the $\delta$~Lyr
  cluster is one of $\sim$10$^3$ clusters whose properties have been
  clarified by Gaia.  Many other exoplanet hosts are candidate
  members of these clusters based on kinematics; their ages can
  be confirmed by using the TESS full frame images to
  measure stellar rotation periods.
\end{abstract}

@@

Matching our young star list against stars observed by Kepler revealed that
%two discoveries.  The first, to be discussed in an upcoming analysis
%by J.~Curtis et al{.}, is that Kepler observed the $\approx$350\,Myr
%open cluster Theia~520 (UBC~1).  At least six Kepler planets are known
%in the cluster from the Kepler-52 and Kepler-968 systems
%\citep{rowe_validation_2014,jontof-hutter_following_2021}.  The second
%discovery, and the focus of this work, is
Kepler observed a portion of the \cn\ (Stephenson-1;
Theia~73).
More specifically, a clustering analysis of the Gaia
data by \citet{kounkel_untangling_2019}
reported that Kepler~1627 (KIC 6184894; KOI 5245; TIC 120105470) is a
\cn\ member.  Given the
previous statistical validation of the close-in mini-Neptune Kepler
1627b
\citep{2012ApJS..199...24T,morton_false_2016,thompson_planetary_2018},
we begin by examining the properties of the cluster more
closely (Section~\ref{sec:cluster}).  We find that the $\delta$ Lyr
cluster is \clusterage\ old, and 
in 
Section~\ref{sec:stars} show
that \sn\ is both a binary and also a member of the cluster.
Focusing on the planet (Section~\ref{sec:planet}), we confirm that despite the
presence of the previously unreported M2.5V companion, hereafter
Kepler\,1627B, the planet orbits the G-dwarf primary, Kepler\,1627A.  Based on a correlation between the
planetary transit times and the local light curve slope, the orbit
may also be prograde.  We conclude by highlighting broader
implications for our ability to age-date a larger sample of planets
(Section~\ref{sec:conc}).

@@

\begin{figure*}[t]
	\begin{center}
		\leavevmode
		\includegraphics[width=1\textwidth]{f6.pdf}
	\end{center}
	\vspace{-0.7cm}
	\caption{
		{\bf Galactic positions and tangential velocities of stars in the
			$\delta$\,Lyr cluster.} Points are reported cluster members from
		\citet{kounkel_untangling_2019}.  
		The tangential velocities relative to
		\sn\ (lower-right) are computed assuming that every star has the same
		three-dimensional spatial velocity as \sn.
		Our analysis uses stars (black points)
		in the spatial and kinematic vicinity of Kepler\,1627 (yellow
		star).  The question of whether the other candidate cluster members
		(gray points) are part of the cluster is outside our scope.  The
		location of the Sun is ($\odot$) is shown.
		\label{fig:XYZvtang}
	}
\end{figure*}

To measure the age of the $\delta$ Lyr cluster, we first selected
a set of candidate cluster members
(Section~\ref{sec:kinematicselection}), and then analyzed these stars using a
combination of the isochronal and gyrochronal techniques
(Section~\ref{sec:clusterage}).

\subsection{Selecting Cluster Members}
\label{sec:kinematicselection}

\citet{kounkel_untangling_2019} applied an unsupervised clustering
algorithm to Gaia DR2 on-sky positions, proper motions, and
parallaxes for stars within the nearest kiloparsec.  For the \cn\
(Theia 73), they reported \noriginal\ candidate members.  We
matched these stars against the latest Gaia EDR3 observations using
the \texttt{dr2\_neighbourhood} table from the ESA archive\footnote{See
\url{https://gea.esac.esa.int/archive/documentation/GEDR3/Gaia_archive/chap_datamodel/sec_dm_auxiliary_tables/ssec_dm_dr2_neighbourhood.html}.},
and took the closest proper motion and epoch-corrected angular
distance as the presumed match
\citep{gaia_collaboration_2021_edr3}.  In Figure~\ref{fig:XYZvtang},
have shown galactic positions only for the stars with
parallax signal-to-noise exceeding 20.  The reported cluster members
(gray and black points) extend over a much larger volume than the
cluster previously identified by \citet{stephenson_possible_1959} and
later corroborated by \citet{eggen_photometric_1968}.  While the
non-uniform ``clumps'' of stars might comprise a {\it bona fide}
cluster of identically-aged stars, they could also be significantly
contaminated by field stars.  We therefore considered stars only in
the immediate kinematic and spatial vicinity of \sn\ as candidate
cluster members.  We performed the selection cuts manually, by
drawing lassos with the interactive \texttt{glue} visualization tool
\citep{beaumont_2014_13866} in the four projections shown in
Figure~\ref{fig:XYZvtang}.  The overlap between the Kepler
field and the resulting candidate cluster members is shown in
Figure~\ref{fig:skychart}.  While this method will
include some field interlopers in the ``cluster star'' sample, and
vice-versa, it should suffice for our aim of verifying the existence
of the cluster in the vicinity of \sn.

\begin{figure}[t]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.47\textwidth]{f1.pdf}
	\end{center}
	\vspace{-0.7cm}
	\caption{
		{\bf Kepler's view of the $\delta$~Lyr cluster.} Each black circle is a
		candidate cluster member, selected from the catalog of \citet{KounkelCovey2019} based on its
		position and kinematics.
		Of the \nkinematic\ candidate cluster members, 58 have at least one
		quarter of Kepler data.  TESS has also observed most of the
		cluster, for one to two lunar months to date.
		\label{fig:skychart}
	}
\end{figure}

\subsection{The Cluster's Age}
\label{sec:clusterage}

@@

\subsubsection{Color-Absolute Magnitude Diagram}
\label{sec:camd}

We measured the isochrone age using an empirical approach.  The left
panel of Figure~\ref{fig:age} shows the color-absolute magnitude
diagram (CAMD) of candidate \cn\ members, IC\,2602, the Pleiades, and the
field.  
The stars from the Pleiades and IC\,2602 were adopted from
\citet{cantatgaudin_gaia_2018}, and the field stars are from the Gaia
EDR3 Catalog of Nearby Stars \citep{gaia_gcns_2021}.  We cleaned these
following the data filtering criteria from
\citet[][Appendix B]{GaiaCollaboration2018}, except that we weakened the parallax
precision requirement to $\varpi/\sigma_\varpi>5$.  These filters were
designed to include genuine binaries while omitting instrumental
artifacts.  We then corrected for extinction by querying the
3-dimensional maps of \citet{capitanio_threedimensional_2017} and
\citet{lallement_threedimensional_2018}\footnote{\url{https://stilism.obspm.fr/}, 2021/09/25},
and applied the extinction coefficients $k_X\equiv A_X/A_0$
computed by \citet{GaiaCollaboration2018} assuming that $A_0 = 3.1
E(B-V)$.  For IC\,2602, the Pleiades, and the \cn, this procedure
yielded a respective mean and standard deviation for the reddening of
$E(B-V)=\{0.020\pm0.003, 0.045\pm0.008, 0.032\pm0.006\}$.  These
values agree reasonably well with previously reported values from the
literature \citep[{\it
e.g.},][]{GaiaCollaboration2018,kounkel_untangling_2019,bossini_age_2019}.

@@

The ages returned by this procedure depend on the ages assumed for
each reference cluster.  We adopted a 115\,Myr age for the Pleiades \citep{dahm_2015},
and a 16\,Myr age for UCL \citep{pecaut_star_2016}.  The age
of IC\,2602 however is the most important ingredient, since it
receives the most weight in the interpolation.  Plausible ages for
IC\,2602 span 30\,Myr to 46\,Myr, with slightly older ages being
preferred by the lithium-depletion-boundary (LDB) measurements 
\citep{dobbie_ic_2010,randich_gaiaeso_2018}
and
younger ages by the main-sequence turn-off
\citep{stauffer_rotational_1997,david_ages_2015,bossini_age_2019}.
If we were to adopt the 30\,Myr age for IC\,2602, then the \cn\ would
be $31^{+5}_{-4}$\,Myr old.  For the converse extreme of 46\,Myr, the
\cn\ would be $44^{+8}_{-7}$\,Myr old.  We adopt an intermediate
38\,Myr age for IC\,2602, which yields an age for the \cn\ of
\clusterage.\footnote{Our exploration of the PARSEC and MIST isochrone
models over a grid of ages, metallicities, and reddenings, yielded the
best agreement for this $\approx 38\,$Myr age as well, given ${\rm
[Fe/H] = +0.1}$ and $A_V=0.2$
\citep{bressan_parsec_2012,choi_mesa_2016};  this preferred CAMD
reddening is higher than the \citet{lallement_threedimensional_2018}
value by a factor of two.  } Follow-up studies of the LDB or
main-sequence turn-off in the \cn\ could help determine a more precise
and accurate age for the cluster, and are left for future work.

\subsubsection{Stellar Rotation Periods}

@@

We then cleaned the candidate TESS rotation period measurements
through a combination of automated and manual steps.  As a matter of
scope, we restricted our attention to the \nkinwithtess\ stars
discussed in Section~\ref{sec:kinematicselection} in the spatial and
kinematic proximity of Kepler\,1627.  To avoid blending, we also only
focused on stars for which no companions were known with a brightness
exceeding one-tenth of the target star in a $21\farcs0$ radius.  There
were \nkinwithtessandcrowding\ stars that met these requirements, and
that had TESS data available.  For plotting purposes we then imposed a
selection based on the strength of the signal itself: we required the
Lomb Scargle power to exceed 0.2, and the period to be below 15\,days.

The lower panel of Figure~\ref{fig:age} shows the resulting
\nkindefaultcleaning\ stars.  The majority of these stars fall below
the ``slow sequence'' of the Pleiades, consistent with a gyrochronal
age for the \cn\ below 100\,Myr.  In fact, the rotation-color
distributions of other 30\,Myr to 50\,Myr clusters ({\it e.g.},
IC\,2602 and IC\,2391) are indistinguishable
\citep{douglas_stephanie_t_2021_5131306}. 
Approximately 10 of the \cn\ stars appear as outliers above
the ``slow sequence''.  Assuming that they are all false positives
({\it i.e.}, field interlopers), our rotation period detection
fraction would be $\nrotgood/\nkinwithtessandcrowding \approx
\nfracprot\%$.   
The other stars are likely to be field contaminants.
A final possible confounding factor -- binarity -- is known to affect
the density of stars that fall beneath the slow sequence
\citep{meibom_effect_2007,gillen_ngts_2020,bouma_2021_ngc2516}.  We do
not expect it to change the central conclusion regarding the cluster's
age.

\section{The Stars}
\label{sec:stars}

\subsection{Kepler\,1627A}
\subsubsection{Age}
Based on the spatial and kinematic association of \sn\ with the \cn,
and the assumption that the planet formed shortly after the star, it
seems likely that \sn\ is the same age as the cluster. There are
two consistency checks on whether this is true: rotation and lithium.  Based on the Kepler
light curve, the rotation period is $2.642\pm0.042$\,days, where the
quoted uncertainty is based on the scatter in rotation periods
measured from each individual Kepler quarter.  This is consistent with
comparable cluster members (Figure~\ref{fig:age}).

To infer the abundance of Li\,\textsc{I} from the 6708\,\AA\ doublet
\citep[{\it e.g.},][]{soderblom_ages_2014}, we acquired an iodine-free
spectrum from Keck/HIRES on the night of 2021 March 26 using the
standard setup and reduction techniques of the California Planet
Survey \citep{howard_cps_2010}.  Following the equivalent width
measurement procedure described by \citet{bouma_2021_ngc2516}, we find
${\rm EW}_{\rm Li} = 233^{+5}_{-7}$\,m\AA.   This value does not
correct for the Fe\,\textsc{I} blend at 6707.44\AA.  Nonetheless,
given the stellar effective temperature (Table~\ref{tab:starparams}),
this measurement is in agreement with expectations for a
$\approx40$\,Myr star ({\it e.g.}, as measured in IC~2602 by
\citealt{randich_gaiaeso_2018}).  It is also larger than any lithium
equivalent widths measured by \citet{berger_identifying_2018} in their
analysis of 1{,}301 Kepler-star spectra.

\subsubsection{Stellar Properties}

The adopted stellar parameters are listed in
Table~\ref{tab:starparams}.  The stellar mass, radius, and effective
temperature are found by interpolating against a 38$\,$Myr MIST
isochrone \citep{choi_mesa_2016}.  
The statistical uncertainties are propagated from the absolute
magnitude (mostly originating from the the parallax uncertainty) and the color; the systematic
uncertainties are taken to be the difference between the PARSEC
\citep{bressan_parsec_2012} and MIST isochrones.  Reported
uncertainties are a quadrature sum of the statistical and systematic
components.
As a consistency check, 
we analyzed the aforementioned Keck/HIRES spectrum from
the night of 2021 March 26 using a combination of
\texttt{SpecMatch-Emp} for stellar properties, and
\texttt{SpecMatch-Synth} for $v\sin i$
\citep{yee_SM_2017}.
This procedure yielded
$T_{\rm eff}=5498\pm100\,{\rm K}$,
$\log g=4.6\pm0.1$, $[{\rm Fe/H}]=0.15\pm0.10$ 
from \texttt{SpecMatch-Emp}, and $v\sin i = 18.9\pm1.0$ from
\texttt{SpecMatch-Synth}.
These values are within the $1$-$\sigma$ uncertainties of our adopted values from
the isochrone interpolation.

\subsection{Kepler\,1627B}

\begin{figure*}[tp]
	\begin{center}
		\leavevmode
		\subfloat{
			\includegraphics[width=0.49\textwidth]{f10a.pdf}
			\includegraphics[width=0.48\textwidth]{f10b.pdf}
		}
	\end{center}
	\vspace{-0.5cm}
	\caption{
    {\bf Kepler 1627 is a binary.} {\it Left:} High-resolution imaging
    from Gemini-North/`Alopeke and Keck/NIRC2 shows an $\approx$M2.5V
    companion at $\rho \approx 0\farcs16$, which corresponds to a
    projected separation of $53\pm4$\,AU.  The inset shows a cutout of
    the stacked NIRC2 image (North is up, East is left, scale is set by the
    separation of the binary).  The lines show 5-$\sigma$ contrast
    limits for the `Alopeke filters, and 6-$\sigma$ contrast limits
    for NIRC2 outside of $0\farcs15$. {\it Right:} Gaia
    EDR3 renormalized unit weight error (RUWE) point estimates for
    candidate $\delta$\,Lyr cluster
    members from Figure~\ref{fig:XYZvtang}.  Since other members of the
    cluster with similar brightnesses have comparable degrees of
    photometric variability, the high RUWE independently suggests that Kepler\,1627
    is a binary. 
    \label{fig:kep1627binary}
	}
\end{figure*}

We first noted the presence of a close neighbor in the \sn\ system on 2015 July 22 when
we acquired adaptive optics imaging using the NIRC2 imager on
Keck-II.
We used the narrow camera (FOV = 10.2\arcsec) to obtain 8
images in the $K'$ filter ($\lambda = 2.12\,\mu$m) with a total
exposure time of 160\,s. We analyzed these data following
\citet{kraus_impact_2016}, which entailed using PSF-fitting to measure the separation,
position angle, and contrast of the candidate companion. 
The best-fitting empirical PSF template was identified from among the
near-contemporaneous observations of single stars in the same filter.
The mean values inferred from the 8 images are reported in
Table~\ref{tab:starparams}.
To estimate the detection limits, we analyzed the residuals after subtracting
the empirical PSF template. Within each residual
image, the flux was measured through 40\,mas apertures centered on
every pixel, and then the noise as a function of radius was estimated
from the RMS within concentric rings. Finally, the detection limits
were estimated from the strehl-weighted sum of the detection
significances in the image stack, and we adopted the $6$-$\sigma$
threshold as the detection limit for ruling out additional companions.

Figure~\ref{fig:kep1627binary} summarizes the results of the
high-resolution imaging.  The Gaia EDR3 parallax for the primary
implies a projected separation of $53 \pm 4$\,AU, assuming the
companion is bound.  Although the companion is unresolved in the Gaia
source catalog (there are no comoving, codistant candidate companions
brighter than $G < 20.5$ mag within $\rho < 120\arcsec$), its
existence was also suggested by the primary star's large renormalized unit weight error (RUWE),
relative to other members of the \cn.  Based on the apparent
separation, the binary orbital period is of order hundreds of years.
The large RUWE is therefore more likely to be caused by a PSF-mismatch
skewing the Gaia centroiding during successive scans, rather than true
astrometric motion.  Regardless, given the low geometric probability that a companion imaged at
$\rho \approx 0\farcs16$ is a chance line-of-sight companion, we
proceed under the assumption that the companion is bound, and that
Kepler\,1627 is a binary.  
Given the distance and age, the models of
\citet{baraffe_new_2015} imply a companion mass of $M_{\rm B} \approx
0.33 M_{\odot}$ and companion temperature of $T_{\rm eff,B} \approx
3450$ K.  The corresponding spectral type is roughly M2.5V
\citep{pecaut_mamajek_2013}.
% \footnote{\url{http://www.pas.rochester.edu/~emamajek/EEM_dwarf_UBVIJHK_colors_Teff.txt}, version \texttt{2021/03/02}.}
These models combined with the NIRC2 contrast limits similarly imply
physical limits on tertiary companions of $M_{\rm ter} < 50
M_{\rm Jup}$ at $\rho = 50$\,AU, $M_{\rm ter} < 20 M_{\rm Jup}$ at $\rho =
100$\,AU, and $M_{\rm ter} < 10 M_{\rm Jup}$ at $\rho = 330$\,AU.

@@

		\vspace{-0.2cm}	
		\subfloat{
			\includegraphics[width=0.5\textwidth]{f3b.pdf}
			\includegraphics[width=0.5\textwidth]{f3c.pdf}
		}
	\end{center}
	\vspace{-0.7cm}
  \caption{ {\bf The light curve of Kepler\,1627.}
    {\it Top}: 
    The Kepler data span 1{,}437 days (3.9 years), sampled at
    30 minute cadence;  a 100 day segment is shown.  The
    top panel shows the \texttt{PDCSAP} median-subtracted flux in
    units of parts-per-thousand ($\times 10^{-3}$).  The dominant
    signal is induced by starspots.  The stellar
    variability model (orange line) is subtracted below, revealing the
    transits of \pn.  The
    online Figure Set spans the entire 3.9 years of observations.
    {\it Bottom}:
    Phase-folded transit of Kepler 1627Ab with stellar variability
    removed.  Windows over 20 hours ({\it left}) and the entire orbit
    ({\it right}) are shown, and the residual after subtracting the
    transit is in the bottom-most row.  The 2-$\sigma$ model uncertainties
    and the best-fit model are the light purple band and the dark
    purple line.  Gray points are individual flux measurements; black
    points bin these to 20 minute intervals, and have a representative
    1-$\sigma$ error bar in the lower right of each panel.  The asymmetric
    residual during transit is significantly larger than the out-of-transit scatter.
    \label{fig:lc}
  }
\end{figure*}

\subsection{Kepler Light Curve}

The Kepler space telescope observed \sn\ at a 30-minute cadence from
2009 May 2 until 2013 April 8.  Data gaps during quarters 4, 9, and 13
led to an average duty cycle over the 3.9~year interval of 78\%.  \sn\
was also observed at 1-minute cadence from 2012 Oct 5 until 2013 Jan
11.  The top panel of Figure~\ref{fig:lc} shows a portion of the 30-minute
cadence \texttt{PDCSAP} light curve.  Nonastrophysical variability has
been removed using the methods discussed by
\citet{smith_kepler_PDC_2017}; the default optimal aperture was
assumed \citep{smith_finding_2016}. 
Cadences with non-zero quality flags (9\% of the data) have been omitted.
 The resulting photometry is dominated by
a quasi-periodic starspot signal with a peak-to-peak amplitude that
varies between 2\% and 8\%.  
Previous analyses have identified and
characterized the hidden transit signal
\citep{2012ApJS..199...24T,thompson_planetary_2018}, validated its
planetary nature \citep{morton_false_2016}, and even searched the
system for transit timing variations \citep{holczer_transit_2016}.
Nonetheless, since the cluster membership provides us
with more precise stellar parameters than those previously available,
we opted to reanalyze the
light curve.

We fitted the Kepler long cadence time series with a model that
simultaneously included the planetary transit and the stellar
variability.  The stellar variability was modeled with the
\texttt{RotationTerm} Gaussian Process kernel in \texttt{exoplanet}
\citep{exoplanet:exoplanet}.  This kernel assumes that the variability
is generated by a mixture of two damped simple harmonic oscillators
with characteristic frequencies set by 1/$P_{\rm rot}$ and its first
harmonic.  We additionally included a jitter term to inflate
the flux uncertainties in a manner that accounted for otherwise
unmodeled excess white noise, and let the eccentricity float.  For
the limb-darkening, we assumed a quadratic law, and sampled using the
uninformative prior suggested by \citet{exoplanet:kipping13}.

Our model therefore included 10 free parameters for the transit ($\{P,
t_0, R_{\rm p}/R_\star, b, u_1 ,u_2 ,R_\star, \log g, e, \omega \}$),
2 free parameters for the light curve normalization and a white noise 
jitter ($\{\langle f \rangle, \sigma_f \}$), and 5
hyperparameters for the GP ($\{\sigma_{\mathrm{rot}},
P_{\mathrm{rot}}, Q_0, \mathrm{d}Q, f \}$).  We also considered
including an additive \texttt{SHOTerm} kernel to account for
stochastic noise, but found that this did not significantly affect the
results, and so opted for the simpler GP kernel.  We fitted the models
using \texttt{PyMC3} \citep{salvatier_2016_PyMC3,exoplanet:theano},
and accounted for the finite integration time of each exposure in the
numerical integration when evaluating the model light curve
\citep[see][]{kipping_binning_2010}.  We assumed a Gaussian
likelihood, and after initializing each model with the parameters of
the maximum {\it a posteriori} model, we sampled using
\texttt{PyMC3}'s gradient-based No-U-Turn Sampler
\citep{hoffman_no-u-turn_2014} in the bases indicated in
Table~\ref{tab:posterior}.  We used $\hat{R}$ as our convergence
diagnostic \citep{gelman_inference_1992}.
